Errorless irrationality: removing error-driven components from the inverse base-rate effect paradigm

### 2023-04-17 docs/manuscript.tex
final copy

% \cogscifinalcopy % Uncomment this line for the final submission

@@

\author{{\large \bf Lenard Dome (lenarddome@gmail.com)} \\
  Brain Research and Imaging Centre \\
  University of Plymouth, Research Way, Plymouth, PL6 8BU
  \AND {\large \bf Andy J. Wills (andy.wills@plymouth.ac.uk)} \\
  Brain Research and Imaging Centre \\
  University of Plymouth, Research Way, Plymouth, PL6 8BU}

@@

We have made available the two experiments written in javascript, the analysis code, the raw data, and all other supplementary materials.
Experiment 1 is shared via \href{https://osf.io/auwvt/?view_only=2dc8384074fa4bcf9f2e3937fdaee2b4}{OSF}, and \href{TBA}{GitHub}.
Experiment 2 is shared via \href{https://osf.io/2tmc4/?view_only=489ebc888ef84a6b9b904072cfbe74df}{OSF} and \href{TBA}{Github}.
The main repository that includes this manuscript and links to the materials for the two experiments can be found on \href{TBA}{GitHub}.
GitHub links will be inserted when document is deanonymized.

@@

The data for Experiment 1 was collected as part of a final-year undergraduate project. We thank for the help and contributions of [to be added on deanonymization of paper].

>>>>

\cogscifinalcopy % Uncomment this line for the final submission

@@

\author{{\large \bf Lenard Dome (lenarddome@gmail.com)} \\
  {\large \bf Andy J. Wills (andy.wills@plymouth.ac.uk)} \\ \\
  School of Psychology \\
  University of Plymouth, Research Way, Plymouth, PL6 8BU}

@@

We have made available the two experiments written in javascript, the analysis code, the raw data, and all other supplementary materials.
Experiment 1 is shared via \href{https://osf.io/auwvt/}{https://osf.io/auwvt/}, and \href{https://github.com/lenarddome/ply216-observational-ibre}{https://github.com/lenarddome/ply216-observational-ibre}.
Experiment 2 is shared via \href{https://osf.io/2tmc4/}{https://osf.io/2tmc4/} and \href{https://github.com/lenarddome/ply222-non-causal-ibreBA}{https://github.com/lenarddome/ply222-non-causal-ibre}.
The main repository that includes this manuscript and links to the materials for the two experiments can be found on \href{https://github.com/lenarddome/pu093-errorless-attentionless-ibre}{https://github.com/lenarddome/pu093-errorless-attentionless-ibre}.

@@

The data for Experiment 1 was collected as part of a final-year undergraduate project. We thank for the help and contributions of Selena Lockett and Charlotte Hubbard in the data collection for Experiment 1.
